\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pifont}
\usepackage{parskip}
\usepackage[hidelinks,colorlinks=true,linkcolor=catblue,urlcolor=catblue]{hyperref}

\definecolor{catblue}{RGB}{20,60,110}
\definecolor{catgray}{RGB}{90,90,90}
\definecolor{catred}{RGB}{150,30,30}
\definecolor{catlight}{RGB}{236,240,247}

\titleformat{\section}{\Large\bfseries\color{catblue}}{\thesection.}{0.6em}{}
\titleformat{\subsection}{\large\bfseries\color{catblue}}{\thesubsection}{0.6em}{}
\titleformat{\subsubsection}{\normalsize\bfseries\color{catgray}}{\thesubsubsection}{0.6em}{}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\fancyhead[L]{\small\color{catgray}CAT DILR Full-Corpus Inference Report}
\fancyhead[R]{\small\color{catgray}ExamIQ Platform}
\fancyfoot[C]{\thepage}

\newcommand{\xmark}{\ding{55}}
\newcommand{\cmark}{\ding{51}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcommand{\rejectitem}[1]{\item[\textcolor{catred}{\xmark}] #1}

\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.22}

% small font helper for big tables
\newcommand{\invtab}{\footnotesize}

\begin{document}

% ===================== TITLE PAGE =====================
\begin{titlepage}
\thispagestyle{empty}
\vspace*{1.2cm}
\begin{center}
{\color{catblue}\rule{\textwidth}{2pt}}\\[0.5cm]
{\Huge\bfseries\color{catblue} CAT DILR\\[0.2cm] Full-Corpus PYQ\\[0.2cm] Inference Report}\\[0.5cm]
{\large\color{catgray} Reverse-engineering the reasoning architecture of CAT DILR\\ across nine years (2017--2025), and a build specification\\ for a CAT-grade DILR generator}\\[0.4cm]
{\color{catblue}\rule{\textwidth}{2pt}}\\[1.6cm]

\begin{tabular}{rl}
\textbf{Prepared for} & ExamIQ Platform --- DILR Generation Initiative\\[0.3cm]
\textbf{Corpus} & \texttt{CAT PYQ.pdf} (2017--2025, 693 pp)\\
 & + CAT 2025 Slot 1/2/3 solved papers\\[0.15cm]
\textbf{Coverage} & 24 DILR slot-sections, $\sim$129 DILR sets, 2017--2025\\[0.3cm]
\textbf{Status} & Inference \& specification document\\
 & No practice questions, mocks, or new sets are generated\\[0.3cm]
\textbf{Date} & 10 June 2026\\
\end{tabular}

\vfill
{\small\color{catgray} Confidential --- internal engineering document. Structures and reasoning patterns only;\\ no CAT question is reproduced verbatim.}
\end{center}
\end{titlepage}

\tableofcontents
\newpage

% ===================== 1. EXEC SUMMARY =====================
\section{Executive Summary}

This report rebuilds the previous DILR inference, which analysed only CAT 2025 (three slots, 15 sets, one year). \textbf{This version analyses the full historical corpus --- $\sim$129 DILR sets spanning CAT 2017 through 2025} --- with \texttt{CAT PYQ.pdf} as the primary expansion and the three 2025 solved papers providing solution-grade depth.

The expansion reinforces the earlier central thesis: \textbf{a CAT DILR set is a hidden object the student must reconstruct, not information to be read.} But several secondary conclusions were \textbf{overfit to 2025}:

\begin{enumerate}[leftmargin=1.6em]
\item \textbf{``Venn / set-theory sets are gone''} --- false. Venn is the \textbf{6th most common family (12 sets, $\sim$9\%)}, a per-slot staple in 2018, 2020 and 2022; it merely sat out 2021, 2023 and 2025.
\item \textbf{``Tournaments don't appear''} --- false. \textbf{Tournament / score-reconstruction is a recurring family (8 sets)}: Hi-Lo bidding, betting-pairs, javelin, archery, rifle, the Chango knockout, the QUIET schedule, and 2025's promote-demote set.
\item \textbf{``Calculation is never the whole step''} --- overstated. The corpus has a real vein of \textbf{near-pure quant-DI} (2023 broadly; 2024 GDP/candlestick/bubble). \textbf{quant-DI is the single most common surface family (22 sets, $\sim$17\%).}
\item An entire engine class --- \textbf{number-theory / cipher reconstruction} (cryptarithms, letter$\to$digit ciphers, prime-product allocation) --- recurs in 2018--2022 and was \textbf{invisible to the 2025-only view}.
\end{enumerate}

The corpus also reveals a \textbf{structural era-shift}: 2017--2019 ran \textbf{8 sets / 32 questions per slot} with high arithmetic intensity and number-theory engines; 2020 was a transition; 2021--2025 settled at \textbf{4--5 sets / 20--22 questions per slot}, hybrid-first and deeper per set.

% ===================== 3. SOURCE COVERAGE =====================
\section{Source Coverage (summary)}

Full detail is in \texttt{source\_coverage\_table.md}. All four mandatory PDFs were detected in \texttt{sources/cat\_pyqs/}, are readable, carry real text layers (no OCR), and are included.

\begin{center}
\begin{tabular}{lccll}
\toprule
\textbf{File} & \textbf{Pages} & \textbf{DILR} & \textbf{Years} & \textbf{Role} \\
\midrule
\texttt{CAT PYQ.pdf} & 693 & 24 sections & 2017--2025 & \textbf{Primary corpus} ($\sim$129 sets) \\
2025 Slot-1 Q-Sol & 28 & Section II & 2025 S1 & Solution-grade (5 sets) \\
2025 Slot-2 Q-Sol & 28 & Section II & 2025 S2 & Solution-grade (5 sets) \\
2025 Slot-3 Q-Sol & 32 & Section II & 2025 S3 & Solution-grade (5 sets) \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Gate: PASSED} --- \texttt{CAT PYQ.pdf} present, readable, and the analytical backbone. Limitation: 2017--2024 are questions-only (no examiner solutions), so casework for those years is structurally inferred and tagged \emph{(inf)}; CAT 2025 solutions calibrate that inference.

% ===================== 4. METHODOLOGY =====================
\section{Methodology}
\begin{enumerate}[leftmargin=1.6em]
\item \textbf{Source gate first.} Inspected \texttt{sources/cat\_pyqs/}, verified all four PDFs, confirmed text layers with PyMuPDF. No analysis before the gate passed.
\item \textbf{Structural extraction.} \texttt{pdftotext -layout} on every file; for \texttt{CAT PYQ.pdf}, year blocks and section headers located programmatically and the 24 DILR sections sliced per slot.
\item \textbf{Per-year classification.} Each section segmented into sets; each set scored on surface family, true engine, visible/hidden/inferable split, casework, a five-axis difficulty vector, ladder character, and CAT-likeness.
\item \textbf{Difficulty vector (L/R/C/D/M), 0--3:} \textbf{L} logic depth, \textbf{R} representation difficulty, \textbf{C} calculation load, \textbf{D} data density, \textbf{M} dynamic movement / feedback.
\item \textbf{Calibration.} CAT 2025 solutions anchored casework patterns; older-year casework inferred from constraint structure and necessity phrasing.
\item \textbf{Integrity.} No question text reproduced; invented labels and structural descriptions only.
\end{enumerate}

% ===================== 5. FINDINGS =====================
\section{Full-Corpus Findings}
\begin{description}[leftmargin=2.2em,style=nextline]
\item[F1 --- The hidden object is universal.] In every set a structure is fully specified in the examiner's mind but only partially exposed; the work is reconstruction.
\item[F2 --- Hybrids dominate, increasingly.] The share of sets whose true engine is an explicit hybrid of two archetypes rises markedly from 2021.
\item[F3 --- Arithmetic is a real difficulty axis --- sometimes the whole axis.] $\sim$40\% of sets carry C$\ge$2; a minority (2023; 2024 GDP/candlestick/bubble) are near-pure quant-DI.
\item[F4 --- Designed indeterminacy is pervasive.] Necessity / ``cannot be determined'' / range answers recur in the majority of sets in every year.
\item[F5 --- Family mix rotates year to year.] No family is guaranteed in a given year, but over a multi-year window all nine families recur. Tuning to one year misses families that sat out.
\end{description}

% ===================== 6. TAXONOMY =====================
\section{Set Family Taxonomy \& Frequency}

Classifying all $\sim$129 sets by \textbf{surface family} (exact tallies from Appendix A):

\begin{center}
\begin{tabular}{lccll}
\toprule
\textbf{Surface family} & \textbf{Sets} & \textbf{Share} & \textbf{Peak years} & \textbf{Absent in} \\
\midrule
quant-DI & 22 & 17\% & 2023, 2024 & --- \\
matrix / grid & 20 & 16\% & 2019, 2020, 2023 & --- \\
distribution / allocation & 19 & 15\% & 2018, 2022, 2025 & --- \\
chart-plus-logic & 19 & 15\% & 2019, 2024, 2025 & --- \\
scheduling & 15 & 12\% & 2017, 2019 & --- \\
Venn / set-theory & 12 & 9\% & 2018, 2020, 2022 & \textbf{2021, 2023, 2025} \\
routes / network & 9 & 7\% & 2017 & 2018, 2020 \\
tournament & 8 & 6\% & 2019, 2021 & 2017, 2018, 2023 \\
dynamic-movement & 3 & 2\% & 2025 & most years \\
hybrid (surface) & 2 & 2\% & 2017--2018 & --- \\
\bottomrule
\end{tabular}
\end{center}

\begin{itemize}[leftmargin=1.4em]
\item The ``big four'' (quant-DI, matrix/grid, distribution, chart-plus-logic) are $\sim$63\% of all sets --- the generator's core output.
\item \textbf{Venn and tournament are not optional} ($\sim$15\% combined, multi-year cycle). The 2025-only report wrongly retired both because both sat out 2025.
\item \textbf{dynamic-movement is rare but high-signal} (M=3 sets): a premium, occasional output, not a staple.
\end{itemize}

\subsection{The structural era-shift}
\begin{center}
\begin{tabularx}{\textwidth}{llcY}
\toprule
\textbf{Era} & \textbf{Sets/slot} & \textbf{Qs/slot} & \textbf{Character} \\
\midrule
2017--2019 & 8 & 32 & High arithmetic; number-theory engines (ciphers, cryptarithms); heavy networks (airline, congestion/Braess); dense necessity culture \\
2020 & 6 & $\sim$24 & Transition; logic flagships (binary-encoding blood-vial, parking simulation); strong Venn \\
2021--2025 & 4--5 & 20--22 & Hybrid-first; fewer but deeper sets; reconstruction fused with arithmetic; movement re-emerges in 2025 \\
\bottomrule
\end{tabularx}
\end{center}
Target the \textbf{modern shape} (4--5 deep hybrid sets/slot) with the \textbf{full-corpus vocabulary}.

% ===================== 7. HIDDEN ENGINE =====================
\section{The Hidden Reasoning Engine}

The ten surface families collapse into a smaller set of true-engine archetypes.

\begin{center}
\begin{tabularx}{\textwidth}{lYY}
\toprule
\textbf{Engine archetype} & \textbf{Reconstructed object} & \textbf{Representative sets (year)} \\
\midrule
Grid / matrix & 2-D table of relationships & platform-height (’17), pouch coins (’19), bead grid (’20), call-ledger (’25) \\
Timeline / sequence & who-does-what-when blocks & dancers (’19), seminars (’20), journals (’21), Gurus (’25) \\
Allocation & distribution of discrete units & inheritance (’17), committees (’18), envy-free (’21), train occupancy (’25) \\
Ranking / score table & ordering, often time-varying & tea-taster (’17), Hi-Lo (’20), promote-demote (’25) \\
Movement system & trajectory through states & parking (’20), patrol (’23), passing-buck \& round-table (’25) \\
Flow network & conserved directed volumes & elective flow (’17), town friendship (’21), trade flows (’25) \\
Venn region-set & counts in overlaps, often ranges & CET (’17), satellites (’18), medicine (’20), travelers (’24) \\
Reconstruct-from-rates & absolutes from ratios/\% & smartphones (’18), store doubling (’19), SI scatter (’25) \\
Number-theory / cipher & code/factorisation forced by arithmetic & cryptarithm (’19), letter cipher (’18), prime funding (’22) \\
\bottomrule
\end{tabularx}
\end{center}

\textbf{Key insight:} the hardest sets are \textbf{hybrids of two archetypes} (train occupancy = allocation + flow network; promote-demote = ranking + feedback; prime funding = allocation + number-theory). A generator that builds only single-archetype objects sits a full difficulty tier below CAT.

% ===================== 8. INFO MODEL =====================
\section{Visible vs Hidden vs Inferable Information}

A deliberate three-layer design, consistent across all nine years:
\begin{enumerate}[leftmargin=1.6em]
\item \textbf{Visible} --- scaffolding: entities, rule, units, a chart, a few anchor facts.
\item \textbf{Hidden} --- the body of the object: most cells, positions, assignments, volumes.
\item \textbf{Inferable-only} --- facts that appear nowhere and emerge only after combining clues; the target of hard/global questions.
\end{enumerate}

\begin{center}
\begin{tabularx}{\textwidth}{lYYY}
\toprule
\textbf{Set (year)} & \textbf{Visible} & \textbf{Hidden} & \textbf{Inferable-only} \\
\midrule
CET percentiles (’17) & ``exactly two'' rule, a ratio, one count & 3-set Venn region sizes & Triple-overlap is a \emph{free variable} $\Rightarrow$ range answer \\
Tea-taster (’17) & doubling/even/min clues & cup$\leftrightarrow$origin$\leftrightarrow$rating bijection & Which statements are only \emph{``may be true''} \\
Parking (’20) & arrival/exit rule, slot map & car type \& occupancy over time & State at a queried moment, per scenario \\
Promote-demote (’25) & leaders, range, tie-break, $\sim$4 ratings & full rating grid + scores + membership & Whose score is \emph{undeterminable} at a quarter \\
Train occupancy (’25) & capacity, few \%, multiples-of-10 & full origin--destination matrix & Counts only the full matrix pins \\
\bottomrule
\end{tabularx}
\end{center}

\textbf{Design principle:} anchor facts must under-determine the object alone and become sufficient only in combination; no single fact resolves a cell directly. The ``NOT determinable / NOT necessarily true'' question type (every year) is the explicit test of layer 3.

% ===================== 9. CASEWORK =====================
\section{Real Casework Analysis}

Casework = the deduction forks, $\ge2$ live hypotheses are carried, and a \textbf{non-local} later clue kills all but one.

\begin{itemize}[leftmargin=1.4em]
\item \textbf{Heavy, genuine casework is the norm} in every year; exceptions cluster in near-pure quant-DI (read-and-compute).
\item \textbf{The killing clue is non-local} --- different condition or later question premise (2025 solutions show this explicitly: the $x{=}7$ tap branch dies on an impossibility three steps away; the $(x{+}60){=}96$ SI branch dies on a lowest-rank condition stated elsewhere).
\item \textbf{At least one branch is seductive} --- arithmetically clean, dying only under a divisibility/parity/range test. This is why \textbf{over-clean arithmetic destroys realism}: nothing for the false branch to die on.
\item \textbf{Designed residual ambiguity} --- many sets are correct but not fully solvable (Venn ranges; ``cannot be determined''; ``may be true'').
\end{itemize}

\begin{center}
\begin{tabularx}{\textwidth}{lY}
\toprule
\textbf{Family} & \textbf{Typical casework} \\
\midrule
matrix/grid, allocation, scheduling, tournament, movement, Venn & \textbf{Heavy} --- forced forks, non-local kills, often residual ambiguity \\
reconstruct-from-rates, number-theory & Medium--heavy --- divisibility/factorisation forks \\
quant-DI (pure), chart read-off & Light / none --- the arithmetic is the point \\
\bottomrule
\end{tabularx}
\end{center}

% ===================== 10. DRIVERS =====================
\section{Difficulty Driver Analysis}

\begin{center}
\begin{tabularx}{\textwidth}{lY}
\toprule
\textbf{Driver} & \textbf{Corpus tendency} \\
\midrule
\textbf{L --- logic depth} & High in grid/allocation/scheduling/tournament/movement/number-theory; low in pure quant-DI \\
\textbf{R --- representation} & \textbf{Consistently high ($\ge$2) in most sets} --- choosing how to draw the object is half the battle; the most under-rated driver \\
\textbf{C --- calculation} & Bimodal --- spikes to 3 in quant-DI / reconstruct-from-rates / older arithmetic sets; near 0 in logic flagships \\
\textbf{D --- data density} & Moderate--high in DI/chart sets; high D without high L = textbook DI, not CAT \\
\textbf{M --- movement / feedback} & Rare but decisive (parking ’20, passing-buck/round-table ’25); hardest to fake \\
\bottomrule
\end{tabularx}
\end{center}

\textbf{The stacking law:} CAT-level difficulty comes from stacking $\ge2$ drivers, not cranking one. High on C alone = a calculation drill; high on D alone = textbook DI. Neither is CAT-level.

% ===================== 11. LADDER =====================
\section{The Question Ladder}

\begin{center}
\begin{tabularx}{\textwidth}{lYY}
\toprule
\textbf{Rung} & \textbf{Purpose} & \textbf{Typical form} \\
\midrule
Entry & Reward the first solid deduction & A value that falls out early \\
Medium & Require a partially-built object & A value needing 2--3 chained clues \\
Hard & Require the fully reconstructed object & A value/comparison resolving only at the end \\
Global / conditional / necessity & Test command of the whole structure or robustness & ``For how many\ldots determinable?'', ``NECESSARILY true / CANNOT be true'', ``If X then\ldots'' \\
\bottomrule
\end{tabularx}
\end{center}

The necessity / ``cannot be determined'' rung is present in the majority of sets every year (dominant 2017--2020; central 2024--2025). Pure quant-DI sets are the exception and the easiest family. \textbf{Author a graded ladder with at least one global/necessity question; where the object is under-determined, at least one question must test determinacy.}

% ===================== 12. WHAT CHANGED =====================
\section{What Changed After Including \texttt{CAT PYQ.pdf}}

\subsection{Conclusions that remain valid}
The hidden-object thesis; hybrid-first; representation as the under-rated driver; designed indeterminacy; the stacking law; ``never hand over the graph'' (confirmed by historical network sets: elective flow ’17, town friendship ’21, dean votes ’23).

\subsection{Conclusions that were overfit to 2025}
\begin{center}
\begin{tabularx}{\textwidth}{YY}
\toprule
\textbf{2025-only claim} & \textbf{Full-corpus correction} \\
\midrule
``Venn sets gone $\Rightarrow$ de-prioritise.'' & Venn is the 6th-most-common family (12 sets); staple in 2018/2020/2022; only sat out 2021/2023/2025. \textbf{Keep Venn.} \\
``Tournaments don't appear.'' & Tournament/score-reconstruction recurs (8 sets): Hi-Lo, betting, javelin, archery, rifle, Chango, QUIET, promote-demote. \textbf{First-class family.} \\
``Calculation is never the whole step.'' & Near-pure quant-DI is a real vein (2023; 2024 GDP/candlestick/bubble). quant-DI is the most common surface family (22). Produce a controlled minority of calc-dominant sets. \\
(silent) ``$\sim$4--5 sets/slot is the norm.'' & True now, but 2017--2019 ran 8 sets / 32 Q per slot --- a larger engine vocabulary. \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Historical patterns missing / under-weighted in the 2025-only view}
\begin{itemize}[leftmargin=1.4em]
\item \textbf{Number-theory / cipher} engines (cryptarithm ’19, letter cipher ’18, prime funding ’22) --- an entire class invisible to 2025-only.
\item \textbf{Equilibrium / congestion networks} (2017 four-car Braess-style, airline connectivity) --- game-theoretic flow networks.
\item \textbf{Simulation / state-machine} sets (parking ’20, project-team rotation ’17) --- pure dynamic-state engines.
\item \textbf{Extremal / min-max optimisation} (100-boxes ’19, ATM notes ’18, cab ratings ’20).
\end{itemize}

\subsection{How the generation strategy should change}
\begin{enumerate}[leftmargin=1.6em]
\item Sample families from the full-corpus distribution, not 2025 --- reinstate Venn, tournament, number-theory, simulation, equilibrium-network.
\item Target the modern \emph{shape} (4--5 deep hybrid sets/slot) with the historical \emph{vocabulary}.
\item Add a controlled minority of calculation-dominant quant-DI sets to match CAT's real mix.
\item Make necessity / determinacy questions mandatory.
\end{enumerate}

\subsection{Families to prioritise}
\textbf{Tier 1 (core, every batch):} matrix/grid, distribution/allocation, scheduling/timeline, quant-DI (incl. reconstruct-from-rates).\\
\textbf{Tier 2 (regular rotation):} chart-plus-logic, Venn/set-theory, tournament/score-reconstruction, flow-network.\\
\textbf{Tier 3 (premium, occasional):} dynamic-movement/simulation, number-theory/cipher, equilibrium-network.

% ===================== 13. AI FAILURE =====================
\section{Why Our AI-Generated DILR Failed}

\begin{center}
\begin{longtable}{c l p{11.5cm}}
\toprule
\textbf{\#} & \textbf{Failure mode} & \textbf{Practical rejection signal} \\
\midrule
\endhead
1 & Direct graph/structure reading & A question is answered by quoting the diagram \\
2 & Graph/table handed over & The set ships with the grid/graph drawn \\
3 & Small universe & Hand-solvable in $<60$ s \\
4 & Fake casework & Every ``case'' closes in the next clue \\
5 & One-step deductions & Each clue resolves exactly one cell \\
6 & Over-clean arithmetic & No integer/parity/multiple/range constraint eliminates \\
7 & No hidden object & Cannot name a structure to build that isn't printed \\
8 & No dynamic state & Nothing changes as you deduce (when theme implies it should) \\
9 & No residual ambiguity & One clean world; no honest ``cannot be determined'' \\
10 & Weak question ladder & All questions same difficulty \\
11 & No global/conditional/necessity question & No ``necessarily true''/``if X then'' \\
12 & Answerable directly from given facts & The question restates a printed fact \\
13 & Uniqueness verified but not CAT-likeness & Solver confirms one answer, but the set is one-step/clean/static/ladderless \\
\bottomrule
\end{longtable}
\end{center}

\textbf{The deepest failure is \#13.} Our prior pipeline verified \emph{answer uniqueness} and stopped --- but a set can be unique and still trivial. \textbf{Uniqueness is necessary, not sufficient.} The generator needs a second gate that checks \emph{CAT-likeness} (multi-driver difficulty, forced non-local casework, a hidden object, a proper ladder), not just solvability.

\textbf{On the graph mock:} it fails \#1, \#2, \#3, \#7, \#10 at once. The fix is not ``avoid networks'' but \textbf{``never hand over the network''} --- CAT's network sets (elective flow ’17, town friendship ’21, dean votes ’23, trade flows ’25) reconstruct the network from balances/conservation/aggregates, never drawn.

% ===================== 14. RULES =====================
\section{Full-Corpus Generation Rules}
\begin{enumerate}[leftmargin=1.8em]
\item \textbf{Object-first authoring.} Build the complete hidden object first, then derive clues by deletion + indirection. Never generate clues first.
\item \textbf{Hidden representation.} Do not hand over the final graph/table/grid; if a diagram is shown, the challenge must be reconstructing a further hidden layer behind it.
\item \textbf{Forced casework.} $\ge2$ globally-consistent partial worlds survive past the initial clue reading.
\item \textbf{Non-local clue interaction.} The clue that kills a false case must not be adjacent to the clue that created the fork.
\item \textbf{Multi-driver difficulty (stacking law).} Score $\ge2$ on at least two of \{L,R,C,D,M\}. C-alone or D-alone is rejected.
\item \textbf{Proper question ladder.} Entry + medium + hard + at least one global/conditional/necessity; test determinacy where the object is under-determined.
\item \textbf{Arithmetic that does logical work.} Numbers carry constraints (integer, parity, multiples, distinctness, range) so a clean-but-wrong branch has something to die on.
\item \textbf{Solver-verified determinacy.} A formal solver / enumerator confirms, per question, unique vs intentionally indeterminate.
\item \textbf{AI quality gate (CAT-likeness, not just uniqueness).} A separate judge tries to reject on the checklist, specifically catching ``unique but trivial'' (\#13).
\item \textbf{Family/engine sampling from the full corpus.} Draw from the \S6 distribution (incl. Venn, tournament, number-theory, simulation); target the modern 4--5-set shape.
\end{enumerate}

% ===================== 15. REJECTION CHECKLIST =====================
\section{Rejection Checklist}
\begin{center}\itshape Run on every generated set before PDF rendering. A single tick is an automatic reject.\end{center}
\begin{itemize}[leftmargin=2.2em,label={}]
\rejectitem{Any answer is \textbf{directly readable} from a clue, chart, or graph.}
\rejectitem{\textbf{One early deduction collapses} the whole set.}
\rejectitem{\textbf{No hidden object} must be reconstructed.}
\rejectitem{The final \textbf{graph/table/grid is handed over} (no further hidden layer).}
\rejectitem{\textbf{No real casework} survives past the first clue reading.}
\rejectitem{The \textbf{universe is too small} ($<\sim$60 s by hand).}
\rejectitem{\textbf{Arithmetic is the only difficulty} (C high, L/R/M all low).}
\rejectitem{\textbf{All questions are the same difficulty} (no ladder).}
\rejectitem{\textbf{No question tests global structure.}}
\rejectitem{\textbf{No question tests conditional or necessity} reasoning.}
\rejectitem{\textbf{No question tests determinacy} where the object is intentionally under-determined.}
\rejectitem{The set is \textbf{merely chart reading + calculation}.}
\rejectitem{The \textbf{blind solver solves it too quickly, with no branching}.}
\rejectitem{The \textbf{formal solver cannot verify} uniqueness or intended ambiguity.}
\rejectitem{\emph{(meta)} The set is \textbf{unique but not CAT-like} (passes uniqueness yet trips $\ge3$ above --- failure \#13).}
\end{itemize}

\textbf{Acceptance bar:} no box ticked; rules \S14.1--\S14.10 hold; an independent blind solver reconstructs the object from the prompt alone and reproduces both the intended answers and the intended indeterminacies; the CAT-likeness judge returns accept.

% ===================== 16. PIPELINE =====================
\section{Recommended Terminal Pipeline}

Core principle: \textbf{separate the author from the checkers}, and gate on \textbf{CAT-likeness}, not just uniqueness.

\begin{small}
\begin{verbatim}
 1. SOURCE INGESTION    Place PDFs in sources/cat_pyqs/. Verify text layer; pdftotext.
 2. PYQ SET EXTRACTION  Slice year/slot/section; segment sets; structural digests.
 3. REASONING INFERENCE Classify family+engine+driver vector; corpus dist = sampler prior.
 4. HIDDEN-OBJECT       Sample (family, engine-hybrid, driver target). Build FULL object
    AUTHORING           first, then delete+re-express into clues. Author graded ladder
    (object-first)      incl. a necessity/determinacy question.
 5. BLIND SOLVING       SEPARATE agent (no key) reconstructs object from clues; logs
                        deduction order, branch count, time-to-solve.
 6. FORMAL VERIFICATION z3 / OR-Tools / brute enumeration counts ALL worlds -> per-Q
                        determinacy profile (unique vs intended-ambiguous).
 7. ADVERSARIAL JUDGING SEPARATE judge runs rejection checklist incl. CAT-likeness gate.
                        Any tick -> reject, loop to stage 4 with reasons.
 8. LaTeX / PDF RENDER  Template set.tex + solution.tex; pdflatex (x2 for ToC).
 9. WEBSITE-READY OUT   Emit set.json (prompt, options, answers, determinacy flags) + HTML.
10. STORAGE / INDEXING  content/cat/dilr/<id>/; register in practice DB; index by family,
                        engine, driver vector, difficulty, world-count, ladder profile.
\end{verbatim}
\end{small}

\subsection{Proposed folder structure}
\begin{small}
\begin{verbatim}
content/cat/dilr/
  <set_id>/
    prompt.json        # entities, rule, anchor clues, questions, options
    answer_key.json    # full hidden object + per-question answers + determinacy
    metadata.json      # family, engine, drivers, world-count, judge verdict, provenance
    set.tex set.pdf
    solution.tex solution.pdf
    web.json           # website-ready payload
  _rejected/<set_id>/  # rejected drafts + structured failure reasons
sources/cat_pyqs/      # raw PYQ PDFs (never committed; analysis input only)
reports/dilr_inference_full/  # this report + coverage/extraction logs
\end{verbatim}
\end{small}

\subsection{Metadata to store per set}
\texttt{engine\_archetype}, \texttt{engine\_hybrid\_of[]}, \texttt{surface\_family}, \texttt{driver\_vector \{L,R,C,D,M\}}, \texttt{entity\_count}, \texttt{consistent\_world\_count}, \texttt{casework\_branch\_count}, \texttt{has\_indeterminate\_question}, \texttt{ladder\_profile}, \texttt{blind\_solver\_minutes}, \texttt{blind\_solver\_branches}, \texttt{judge\_verdict}, \texttt{source\_family\_prior}, \texttt{provenance}.

\subsection{Orchestration \& repo hygiene}
One \texttt{dilr\_pipeline.py} (or Claude Code workflow), \texttt{--count N}. Author / Solver / Judge are distinct agents; solver and judge run without the key. Formal verifier: \texttt{z3-solver} / \texttt{ortools} (or brute enumeration). Only stage-7-passing sets reach \texttt{content/}. \textbf{Never} commit/move raw PDFs; never touch app/source, \texttt{next-env.d.ts}, \texttt{tsconfig.json}, package/build config, or \texttt{.next/}.

% ===================== 17. APPENDIX =====================
\section{Appendix A --- Per-Year Set Inventory}

Compact teardown of all $\sim$129 sets. Drivers are L/R/C/D/M (0--3). Casework for 2017--2024 is \emph{(inf)} = inferred from structure; 2025 is solution-calibrated. Labels are invented descriptors --- no question text is reproduced.

\subsection{CAT 2017 (16 sets --- 8/slot; high arithmetic, networks, number-theory)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
Pizzeria type-proportion & quant-DI & matrix (party$\times$type) & light & L1 R2 C3 D2 M0 & partial \\
Elective re-enrollment flow & routes/network & flow-network & heavy & L3 R3 C2 D3 M1 & yes \\
Inheritance asset split & distribution & allocation & heavy & L3 R1 C2 D1 M0 & partial \\
Dorm repair-cost grid & chart-plus-logic & grid & heavy & L3 R2 C1 D2 M0 & yes \\
Tea-taster cup ratings & scheduling & ranking & heavy & L3 R2 C1 D1 M0 & yes \\
Queen attack chessboard & matrix/grid & grid geometry & light & L2 R3 C2 D1 M1 & partial \\
Airline seat pricing & scheduling & allocation & heavy & L3 R2 C3 D3 M0 & yes \\
Fingerprint scan-order count & hybrid & sequence (perm.) & light & L3 R1 C2 D0 M0 & yes \\
Fast-food order scheduling & scheduling & timeline (parallel) & heavy & L2 R2 C2 D2 M2 & yes \\
Rural-kids school survey & quant-DI & 3-way matrix & light--heavy & L2 R2 C3 D3 M0 & partial \\
CET percentile selection & Venn & Venn-regions & heavy & L3 R2 C2 D2 M0 & yes (range) \\
Happiness-index scores & chart-plus-logic & grid (S/F/C) & heavy & L3 R2 C2 D2 M0 & yes \\
Project-team SE/RE rotation & distribution & movement-traj. & heavy & L3 R2 C3 D2 M3 & yes \\
Platform-height reachability & matrix/grid & grid (sightline) & heavy & L3 R3 C1 D2 M0 & yes \\
Airline network connectivity & routes/network & flow-network & heavy & L3 R2 C2 D1 M0 & yes \\
Four-car route equilibrium & routes/network & flow-network (eq.) & heavy & L3 R1 C3 D2 M2 & yes (Braess) \\
\bottomrule
\end{longtable}}

\subsection{CAT 2018 (16 sets --- 8/slot; logic-heavy, Venn $\times2$, ciphers)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
Currency buy/sell inventory & quant-DI & score-table & light & L1 R1 C3 D2 M1 & partial \\
Letter$\to$digit cipher & number-theory & allocation+deduction & heavy & L3 R2 C1 D2 M0 & yes \\
Smartphone share/profit & quant-DI & score-table & none & L0 R1 C3 D1 M0 & no \\
Interview-room arrival log & scheduling & timeline & heavy & L3 R2 C1 D1 M1 & yes \\
Accreditation weights & matrix/grid & score-table (perm.) & heavy & L3 R2 C3 D2 M0 & yes \\
Product portfolio grid & chart-plus-logic & matrix & heavy & L3 R2 C2 D2 M0 & partial \\
Amusement-park tickets & distribution & matrix (age$\times$ticket) & heavy & L2 R2 C3 D3 M0 & yes \\
Sports enrollment Venn & Venn & Venn-regions & heavy & L2 R2 C3 D2 M0 & yes (min/max) \\
$n\times n$ numeral colouring & matrix/grid & grid (king-graph) & light & L3 R0 C2 D1 M0 & partial \\
Recruitment composite scores & quant-DI & score-table & heavy & L3 R2 C3 D2 M0 & yes \\
Multi-layer pie sales & chart-plus-logic & score-table (nested) & light & L1 R1 C3 D2 M1 & no \\
Petrol-pump contamination & scheduling & sequence (positional) & heavy & L3 R2 C2 D2 M0 & yes \\
Satellite purposes & Venn & Venn-regions & heavy & L2 R2 C3 D2 M0 & yes (range) \\
ATM note-dispensing & distribution & allocation (partition) & heavy & L2 R2 C3 D2 M0 & partial \\
Three-committee composition & distribution & matrix & heavy & L3 R2 C3 D2 M0 & yes \\
Students major/minor & matrix/grid & grid (triple-attr.) & heavy & L3 R2 C1 D1 M0 & yes \\
\bottomrule
\end{longtable}}

\subsection{CAT 2019 (16 sets --- 8/slot; sequence/grid, cryptarithm, tournaments)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
Store revenue/cost shares & quant-DI & score-table & heavy & L1 R1 C2 D3 M0 & partial \\
Pouch min-max coins grid & matrix/grid & grid (integer-avg) & heavy & L3 R1 C3 D2 M0 & partial \\
Two-proposal voter survey & Venn & Venn-regions & heavy & L2 R1 C3 D2 M0 & partial \\
Speakers/teams/languages & matrix/grid & grid+allocation & heavy & L3 R2 C3 D1 M0 & partial \\
Doctors rooms/queue tokens & scheduling & timeline (queue) & heavy & L2 R1 C2 D2 M2 & partial \\
Monsoon rainfall vs LPA & chart-plus-logic & score-table (roll.) & light & L1 R1 C2 D1 M0 & partial \\
Faculty MT/ET question order & scheduling & sequence & heavy & L3 R2 C3 D1 M0 & yes \\
Rifle shooting 10 rounds & tournament & score-table (window) & heavy & L3 R3 C3 D2 M0 & partial \\
Cryptarithm 6-digit & number-theory & grid+ranking (carry) & heavy & L3 R1 C3 D2 M0 & partial \\
Dancers/composers order & scheduling & sequence & heavy & L3 R2 C3 D0 M0 & partial \\
100-boxes prize doubling & distribution & allocation (extremal) & heavy & L3 R1 C2 D1 M0 & yes \\
Supermarket 16 shelves & distribution & sequence (cluster) & heavy & L3 R2 C3 D0 M0 & yes \\
Street-map line-of-sight & routes/network & movement-traj. & heavy & L3 R2 C3 D0 M2 & partial \\
Archery bonus rounds & tournament & score-table & heavy & L2 R3 C3 D2 M0 & partial \\
Foreigner-crime ranking DI & chart-plus-logic & score-table+rank & light--med & L1 R3 C2 D1 M0 & partial \\
Five-vendor radar scoring & chart-plus-logic & score-table & none--light & L1 R1 C1 D2 M0 & no \\
\bottomrule
\end{longtable}}

\subsection{CAT 2020 (15 sets --- 5/slot; logic flagships, strong Venn, simulation)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
Pooled blood-vial diagnosis & matrix/grid & matrix+binary-encoding & heavy & L3 R2 C2 D0 M0 & yes \\
Hi-Lo four-player bidding & tournament & score-table & heavy & L3 R2 C2 D2 M0 & yes \\
OTLP 4-facility survey & Venn & Venn-regions (4-set) & light & L1 R1 C1 D3 M0 & partial \\
Two-day grocery delivery & quant-DI & timeline+score-table & light & L1 R2 C0 D3 M0 & partial \\
Farmer's 12-plot land & matrix/grid & grid+allocation & heavy & L3 R2 C2 D2 M1 & yes \\
$5\times5$ tri-colour beads & matrix/grid & matrix+combinatorics & heavy & L3 R2 C3 D0 M1 & partial \\
Doctoral seminar scheduling & scheduling & timeline & heavy & L3 R2 C1 D0 M0 & yes \\
Constituency deposit votes & chart-plus-logic & score-table+quant-DI & light--heavy & L2 R2 C1 D3 M0 & partial \\
Departmental-store sales & quant-DI & matrix (AP fill) & light & L1 R2 C0 D3 M0 & partial \\
Basement compact/SUV parking & dynamic-movement & movement-traj. & heavy & L3 R2 C1 D0 M3 & no \\
Four-medicine groups & Venn & Venn-regions (4-set) & light & L1 R1 C1 D3 M0 & partial \\
Vendor-institute contracts & scheduling & timeline & heavy & L3 R2 C1 D1 M0 & yes \\
Board-exam missed marks & chart-plus-logic & score-table+matrix & heavy & L3 R2 C1 D2 M0 & yes \\
Cab-driver ratings & quant-DI & score-table+allocation & heavy & L2 R2 C2 D2 M0 & partial \\
Ten percussion experts & Venn & Venn-regions+logic & heavy & L3 R2 C1 D0 M0 & yes \\
\bottomrule
\end{longtable}}

\subsection{CAT 2021 (12 sets --- 4/slot; hybrid-first, arithmetic-laced)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
Javelin throw re-ranking & tournament & score-table+rank+timeline & heavy & L2 R3 C2 D3 M1 & yes \\
Reviewer approval routing & distribution & flow-network+grid & heavy & L3 R3 C3 D1 M1 & partial \\
Employee project Gantt & chart-plus-logic & timeline+score-table & light & L1 R2 C1 D3 M1 & no \\
Impurity bottle testing & quant-DI & allocation+flow-network & heavy & L2 R2 C3 D2 M0 & partial \\
Order shipping Gantt & chart-plus-logic & timeline & light & L1 R2 C1 D3 M1 & no \\
Chango knockout bracket & tournament & ranking+flow-network & heavy & L3 R2 C2 D2 M0 & yes \\
Delivery ratings \& bonus & matrix/grid & grid+score-table & heavy & L3 R2 C3 D2 M1 & partial \\
Envy-free object bundles & distribution & allocation+score-table & heavy & L3 R3 C3 D2 M0 & yes \\
Subcategory sales bars & quant-DI & score-table & none--light & L0 R1 C1 D3 M0 & no \\
Smoothie production econ. & quant-DI & allocation+score-table & heavy & L2 R2 C3 D2 M1 & partial \\
Journal paper scheduling & scheduling & grid+timeline & heavy & L3 R3 C3 D2 M1 & yes \\
Town friendship network & routes/network & Venn+flow-network & heavy & L3 R2 C3 D1 M0 & yes \\
\bottomrule
\end{longtable}}

\subsection{CAT 2022 (12 sets --- 4/slot; Venn $\times3$, prime-number allocation)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
CS/non-CS course grades & Venn & Venn-regions & light & L2 R2 C3 D1 M0 & yes \\
Cohort mortality age-bands & quant-DI & timeline & light & L1 R1 C3 D3 M0 & partial \\
Pandemic daily new-cases & distribution & grid (bounded int.) & heavy & L3 R3 C2 D1 M0 & yes \\
Betting-pairs money tracker & tournament & score-table & heavy & L3 R2 C2 D1 M2 & partial \\
Supermarket approvals & Venn & Venn-regions ($2{\times}2{\times}2$) & light & L2 R2 C3 D1 M0 & yes \\
Widget supply routing & routes/network & flow-network & heavy & L2 R2 C2 D3 M2 & partial \\
Four-company revenue/cost & chart-plus-logic & score-table & none & L1 R1 C0 D3 M2 & no \\
TRICCEK door-to-door sales & distribution & grid & heavy & L3 R2 C2 D2 M1 & partial \\
Four players goals/matches & matrix/grid & grid (scoring) & heavy & L3 R3 C2 D1 M0 & yes \\
Prime-token funding & number-theory & matrix (prime-fact.) & heavy & L3 R3 C2 D1 M1 & yes \\
Attendance interest tiers & Venn & Venn-regions (nested) & heavy & L2 R2 C3 D1 M0 & yes \\
Metro line scheduling & scheduling & timeline (map) & light & L2 R2 C1 D1 M3 & partial \\
\bottomrule
\end{longtable}}

\subsection{CAT 2023 (12 sets --- 4/slot; very high arithmetic, ZERO Venn)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
AC dealer variant sales & distribution & grid ($4{\times}2{\times}2$) & light & L1 R1 C1 D3 M3 & partial \\
Course project-test scoring & matrix/grid & score-table+ranking & heavy & L2 R2 C2 D2 M2 & yes \\
Patrol teams street routes & routes/network & movement-traj.+timeline & heavy & L2 R2 C3 D0 M0 & yes \\
Online vs offline registr. & quant-DI & score-table (min/max/med) & heavy & L1 R1 C3 D3 M1 & partial \\
Firms funding rise-fall & quant-DI & sequence & heavy & L1 R2 C3 D3 M0 & yes \\
Draw competition ranks & quant-DI & score-table+ranking & heavy & L1 R2 C3 D3 M0 & yes \\
$3\times3$ coin-sack boxes & matrix/grid & matrix (sums+medians) & heavy & L1 R1 C3 D3 M0 & yes \\
Theme-park rides timing & scheduling & timeline+allocation & heavy & L2 R1 C3 D2 M2 & yes \\
Dean election voting & distribution & flow-network+allocation & heavy & L2 R3 C3 D1 M0 & yes \\
Restaurant worker ratings & quant-DI & score-table (stats) & heavy & L1 R1 C3 D3 M0 & partial \\
Visa office slot processing & scheduling & timeline+flow-network & heavy & L2 R1 C2 D3 M1 & yes \\
Housing-complex pricing & matrix/grid & grid+score-table & heavy & L2 R2 C3 D2 M1 & yes \\
\bottomrule
\end{longtable}}

\subsection{CAT 2024 (15 sets --- 5/slot; chart-plus-logic heavy, Venn returns)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
ATM cash on road grid & routes/network & matrix+allocation & heavy & L2 R2 C3 D2 M0 & yes \\
OTT subscriber app usage & Venn & Venn-regions+quant-DI & light & L1 R2 C1 D3 M0 & partial \\
Country GDP per-capita & quant-DI & score-table & none & L0 R1 C0 D3 M1 & no \\
AC temperature mode graph & chart-plus-logic & timeline & heavy & L2 R3 C3 D2 M3 & yes \\
Foodgrain nutrient comp. & matrix/grid & matrix (incomplete) & heavy & L1 R2 C3 D2 M0 & yes \\
10-number ordered grid & matrix/grid & grid (monotone) & heavy & L3 R3 C3 D0 M0 & yes \\
Gated-area walkway routes & routes/network & flow-network & heavy & L1 R3 C2 D2 M0 & partial \\
E-commerce daily ratings & chart-plus-logic & score-table & light & L1 R2 C1 D3 M0 & partial \\
Firm PAT/ES/PRD bubble & chart-plus-logic & quant-DI & none & L0 R1 C0 D3 M1 & no \\
Gymnasts coach ratings & distribution & allocation+score-table & heavy & L2 R3 C3 D1 M0 & yes \\
QUIET tournament schedule & tournament & timeline & heavy & L2 R3 C3 D0 M0 & yes \\
Travelers' country Venn & Venn & Venn-regions (3-set) & light & L1 R2 C2 D2 M0 & partial \\
Candlestick share prices & chart-plus-logic & quant-DI & none & L0 R1 C0 D3 M1 & no \\
Web surfers' star giving & distribution & allocation & heavy & L1 R3 C3 D2 M0 & yes \\
Election campaign voting & quant-DI & score-table+casework & heavy & L1 R2 C3 D3 M0 & partial \\
\bottomrule
\end{longtable}}

\subsection{CAT 2025 (15 sets --- 5/slot; solution-calibrated; movement returns, ZERO Venn)}
{\invtab
\begin{longtable}{p{3.0cm}p{2.05cm}p{2.5cm}p{1.2cm}p{2.05cm}p{1.7cm}}
\toprule
\textbf{Set} & \textbf{Family} & \textbf{Engine} & \textbf{Casework} & \textbf{Drivers} & \textbf{Ladder} \\
\midrule
\endhead
Operator call-minutes ledger & matrix/grid & matrix+score-table & heavy & L3 R0 C2 D3 M0 & partial \\
Cross-currency traveler costs & quant-DI & allocation+score-table & heavy & L2 R0 C2 D3 M0 & yes \\
Puzzle-solving progress charts & chart-plus-logic & timeline (cross-chart) & light & L1 R0 C1 D3 M1 & partial \\
Three/Five-country trade flows & quant-DI & flow-network & light & L1 R0 C1 D3 M0 & yes \\
Passing-the-Buck circle & dynamic-movement & movement-traj. & heavy & L3 R2 C3 D0 M2 & partial \\
Gurus training timeline & scheduling & timeline (blocks) & heavy & L3 R2 C3 D0 M0 & partial \\
Sustainability-index scatter & chart-plus-logic & score-table+rank (rates) & heavy & L2 R2 C2 D3 M0 & yes \\
State pollution measures & distribution & allocation+ranking & heavy & L3 R2 C2 D2 M0 & partial \\
Co-authorship paper counts & chart-plus-logic & matrix+allocation & heavy & L3 R1 C3 D2 M0 & partial \\
Balls-through-hoops sizing & matrix/grid & matrix+ranking (order) & heavy & L3 R3 C2 D0 M0 & yes \\
Train segment occupancy & distribution & flow-network (O-D) & heavy & L2 R1 C2 D3 M0 & yes \\
Quarterly promote-demote & tournament & score-table+rank (fb) & heavy & L3 R2 C2 D2 M1 & partial \\
Round-table chair moves & dynamic-movement & movement-traj. & heavy & L3 R2 C3 D0 M3 & partial \\
Foot-tap question game & distribution & allocation+score-table & heavy & L3 R0 C3 D2 M0 & partial \\
Five-country tariff charts & quant-DI & flow-network & light & L1 R0 C1 D3 M0 & yes \\
\bottomrule
\end{longtable}}

\vspace{0.6cm}
\begin{center}\textit{End of report.}\end{center}

\end{document}
